---
title: "Climate Change Time Series"
author: "Austin Jia"
date: '2022-03-16'
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Libraries
```{R}
library(xts)
library(ggplot2)
library(dplyr)
library(plotly)
library(hrbrthemes)
library(forecast)
library(GGally)
library(gridExtra)
```

###Reading Data
```{r}
train = read.csv("DailyDelhiClimateTrain.csv")
test = read.csv("DailyDelhiClimateTest.csv")
full = rbind(train, test)

nrow(train)
nrow(test)
```

###Data Wrangling
```{r}
#Converting to 
train$date = as.Date(train$date, format = "%Y-%m-%d")
test$date = as.Date(test$date, format = "%Y-%m-%d")
full$date = as.Date(full$date, format = "%Y-%m-%d")

#Convert first day to day of the year
dayofyear = as.numeric(format(train[1,1], "%j"))
train.ts = ts(train$meantemp, start = c(2013, dayofyear), frequency=365)
test.ts = ts(test$meantemp, start = c(2013, dayofyear), frequency=365)
full.ts = ts(full$meantemp, start= c(2013, dayofyear), frequency=365)
```

###Exploratory Data Analysis
```{r}
max(full$meantemp)
mean(full$meantemp)
full$date[full$meantemp == max(full$meantemp)]

#Overall time-seriesplot
full %>%
  ggplot(aes(x=date, y=meantemp)) +
  geom_line(color="#69b3a2") +
  ylim(0, 50) +
  annotate(geom="text", x=as.Date("2014-01-25"), y=45, label = "Peak of 38.7 degrees in the middle of 2013") +
  annotate(geom = "point", x=as.Date("2013-05-25"), y=38.71429, size = 10, shape=21, fill = "transparent") +
  geom_hline(yintercept = mean(train$meantemp), color = "orange", size = .5) +
  theme_ipsum()

#Seasonal plots
ggseasonplot(full.ts, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("Mean Temperature") +
  xlab("Months") + 
  ggtitle("Seasonal plot: mean temperature")

#Distribution plots with other covariates
GGally::ggpairs(as.data.frame(full[,2:5]))

#Lag plots -- reflects strong seasonality
full2.ts <- window(full.ts, start=2013)
gglagplot(full2.ts, h = 12)

ggAcf(full2.ts)
```

###Forecasting -- No Other Predictors
####Forecasting
```{r}
#Benchmarks of mean, naive, and seasonal naive
autoplot(train.ts) +
  autolayer(meanf(train.ts, h=300),
    series="Mean", PI=FALSE) +
  autolayer(naive(train.ts, h=300),
    series="Na誰ve", PI=FALSE) +
  autolayer(snaive(train.ts, h=300),
    series="Seasonal na誰ve", PI=FALSE) +
  ggtitle("Forecasts for Daily Mean Temperature") +
  xlab("Year") + ylab("Mean Temperature") +
  guides(colour=guide_legend(title="Forecast"))

#Benchmark forecasts with intervals
autoplot(train.ts) + autolayer(meanf(train.ts, h=300),
    series="Mean", PI=TRUE) +
  ggtitle("Forecasts for Daily Mean Temperature") +
  xlab("Year") + ylab("Mean Temperature") +
  guides(colour=guide_legend(title="Forecast"))

autoplot(train.ts) + autolayer(naive(train.ts, h=300),
    series="Naive", PI=TRUE) +
  ggtitle("Forecasts for Daily Mean Temperature") +
  xlab("Year") + ylab("Mean Temperature") +
  guides(colour=guide_legend(title="Forecast"))

autoplot(train.ts) + autolayer(snaive(train.ts, h=300),
    series="Seasonal Naive", PI=TRUE) +
  ggtitle("Forecasts for Daily Mean Temperature") +
  xlab("Year") + ylab("Mean Temperature") +
  guides(colour=guide_legend(title="Forecast"))

#Drift, with bias-adjustment
drift1 = rwf(train.ts, drift=TRUE, lambda=0, h=114, level=50)
drift2 = rwf(train.ts, drift=TRUE, lambda=0, h=114, level=50,
  biasadj=TRUE)
autoplot(train.ts) +
  autolayer(drift1, series="Simple back transformation") +
  autolayer(drift2, series="Bias adjusted", PI=FALSE) +
  guides(colour=guide_legend(title="Forecast"))
```

####Residuals
```{r}
#Mean
checkresiduals(meanf(train.ts))

#Naive
checkresiduals(naive(train.ts))

#Seasonal Naive
checkresiduals(snaive(train.ts))
```

#### Accuracy
```{r}
#Visualization of forecast against test set
meanf <- meanf(train.ts,h=114)
rfw <- rwf(train.ts,h=114)
snaive <- snaive(train.ts,h=114)
autoplot(window(full.ts, start=2013)) +
  autolayer(meanf, series="Mean", PI=FALSE) +
  autolayer(rfw, series="Na誰ve", PI=FALSE) +
  autolayer(snaive, series="Seasonal na誰ve", PI=FALSE) +
  xlab("Date") + ylab("Mean Temperature") +
  ggtitle("Forecasts for daily temperature") +
  guides(colour=guide_legend(title="Forecast"))

#Quantifying errors
test2.ts <- window(full.ts, start=2017)
accuracy(meanf, test2.ts)
accuracy(rfw, test2.ts)
accuracy(snaive, test2.ts)
```

###Time Series Regression
####Data Wrangling
```{r}
full.ts.predictors = ts(full, start=2013, frequency=365)
train.ts.predictors = ts(train, start=2013, frequency=365)
test.ts.predictors = ts(test, start=2017, frequency=365)

colnames(full)
```

####EDA
```{R}
autoplot(full.ts.predictors[,c("meantemp","wind_speed")]) +
  ylab("Y Measurement") + xlab("Year")

autoplot(full.ts.predictors[,c("meantemp","humidity")]) +
  ylab("Y Measurement") + xlab("Year")

autoplot(full.ts.predictors[,c("meantemp","meanpressure")]) +
  ylab("Y Measurement") + xlab("Year")
```

####Modeling
```{R}
#Fitting the Model
fit.predictors <- tslm(
  meantemp ~ humidity + wind_speed + meanpressure,
  data=full.ts.predictors)
summary(fit.predictors)

#Time plot of actual temperatures and predicted temperatures
autoplot(full.ts.predictors[,'meantemp'], series="Data") +
  autolayer(fitted(fit.predictors), series="Fitted") +
  xlab("Year") + ylab("") +
  ggtitle("Mean Temperature") +
  guides(colour=guide_legend(title=" "))

#Actual temperature plotted against predicted temperature
cbind(Data = full.ts.predictors[,"meantemp"],
      Fitted = fitted(fit.predictors)) %>%
  as.data.frame() %>%
  ggplot(aes(x=Data, y=Fitted)) +
    geom_point() +
    ylab("Fitted (predicted values)") +
    xlab("Data (actual values)") +
    ggtitle("Mean Temperature") +
    geom_abline(intercept=0, slope=1)

#Checking Residuals
checkresiduals(fit.predictors)

#Residual plots against predictors -- don't look good!
df <- as.data.frame(full.ts.predictors)
df[,"Residuals"]  <- as.numeric(residuals(fit.predictors))
p1 <- ggplot(df, aes(x=meanpressure, y=Residuals)) +
  geom_point()
p2 <- ggplot(df, aes(x=wind_speed, y=Residuals)) +
  geom_point()
p3 <- ggplot(df, aes(x=humidity, y=Residuals)) +
  geom_point()
gridExtra::grid.arrange(p1, p2, p3, nrow=2)

#Residuals versus fitted values -- violates homoscedasticity
cbind(Fitted = fitted(fit.predictors),
      Residuals=residuals(fit.predictors)) %>%
  as.data.frame() %>%
  ggplot(aes(x=Fitted, y=Residuals)) + geom_point()

CV(fit.predictors)
```

###Time Series Regression with Trend and Season
####Modeling
```{R}
#Fitting the model
fit.trend <- tslm(full.ts ~ trend + season)
summary(fit.trend)

#Visualizing results -- Time plot of actual temperature and predicted temperature
autoplot(full.ts, series="Data") +
  autolayer(fitted(fit.trend), series="Fitted") +
  xlab("Year") + ylab("Megalitres") +
  ggtitle("Quarterly Beer Production")

CV(fit.trend)

#Visualizing 
fcast.trend <- forecast(fit.trend)
autoplot(fcast.trend) +
  ggtitle("Forecasts of mean temperature using regression") +
  xlab("Year") + ylab("megalitres")
```

###Forecasting Through Decomposition
```{R}
#Classical decomposition
full.ts %>% decompose(type="multiplicative") %>%
  autoplot() + xlab("Year") +
  ggtitle("Classical multiplicative decomposition
    of electrical equipment index")

#STL Decomposition
full.ts %>%
  stl(t.window=13, s.window="periodic", robust=TRUE) %>%
  autoplot()

#Modeling through decomposition
fit.stl <- stl(full.ts, t.window=2, s.window="periodic",
  robust=TRUE)
fit.stl %>% seasadj() %>% naive() %>%
  autoplot() + ylab("New orders index") +
  ggtitle("Naive forecasts of seasonally adjusted data")

fit.stl %>% forecast(method="naive") %>%
  autoplot() + ylab("New orders index")
```

###Exponential Smoothing
####Simple Exponential Smoothing
```{R}
fit.ses <- ses(full.ts, h=5)
# Accuracy of one-step-ahead training errors
round(accuracy(fit.ses),2)

#Visualizing predictions
autoplot(fit.ses) +
  autolayer(fitted(fit.ses), series="Fitted") +
  ylab("Mean Temperature") + xlab("Year")

checkresiduals(ses(full.ts))
```

####Holt Method
```{R}
#Fitting
fit.holt <- holt(full.ts, h=500)
round(accuracy(fit.holt),2)

#Dampened Holt
fit.holt.damp <- holt(full.ts, damped=TRUE, phi = 0.9, h=500)
round(accuracy(fit.holt.damp), 2)

#Visualizing Fit
autoplot(full.ts) +
  autolayer(fit.holt, series="Holt's method", PI=FALSE) +
  autolayer(fit.holt.damp, series="Damped Holt's method", PI=FALSE) +
  ggtitle("Forecasts from Holt's method") + xlab("Year") +
  ylab("Mean Temperature") +
  guides(colour=guide_legend(title="Forecast"))

checkresiduals(holt(full.ts))
```

###ARIMA Fitting
```{R}
d.arima <- auto.arima(train.ts)
d.forecast <- forecast(d.arima, level = c(95), h = 50)
autoplot(d.forecast)
checkresiduals(d.arima)

round(accuracy(d.arima),2)
```